### 2018-02-09 Writing/Thesis/content/chapter-fundamentals.tex

This chapter lays out the fundamentals for Firstly,the

\section{Machine Learning}
In this section, the aspects of the field of machine learning which are relevant for this thesis are going to be introduced briefly. The core of machine learning are learning algorithms, which are used to induce a general model from a set of data samples. The concept of machine learning will be explained here with the help of an example. % Further what happens exactly here

@@

\subsection{Classifier Evaluation}

\subsection{Kendall Rank Correlation Coefficient}
% We need to evaluate the ranker quality somehow, ranker predicts rank, so need a 
To evaluate the quality of the prediction that the ranker will make, a statistic is needed to compare a predicted ranking with other rankings like a baseline or an optimal ranking.

@@

As we have seen in example above, can also have same rank for items. In order to account for this, a second statistic, $T_B$ has been defined as

@@

>>>>

The core topic of this thesis falls under the category of machine learning. Thus, firstly the concept of machine learning and the

\section{Machine Learning}
In this section, the aspects of the field of machine learning which are relevant for this thesis are going to be introduced briefly. The core of machine learning is learning algorithms, which are used to induce a general model from a set of data samples. The concept of machine learning will be explained here with the help of an example. % Further what happens exactly here

@@

\subsection{Kendall Rank Correlation Coefficient}
% We need to evaluate the ranker quality somehow, ranker predicts rank, so need a 
To evaluate the quality of the prediction that the ranker will make, a statistic is needed to compare a predicted ranking with other rankings like a baseline or an optimal ranking.  serves as indication of causal connection

@@

As we have seen in example above, can also have same rank for items. In order to account for this, a second statistic, $T_B$ is defined as

@@

\subsection{Loss}
While the Kendall rank correlation coefficient is an indication as to what degree a predicted ranking agrees with the correct ranking of classifiers for a certain data set, it does not convey the difference in performance experienced by the user when choosing the first of the recommended algorithms. This difference can b expressed in measure called loss \cite{DBLP:conf/mldm/LeiteBV12}, which is defined as the difference of the performance of the actual best algorithm and the actual performance of the first recommended algorithm.

Additionally, the ranker recommends a ranking instead of a single algorithm in order to allow a user (or automated tool) to test a few of the top-ranked algorithms, which therefore also needs to be taken into account when thinking about loss. This is done here by computing a measure called best three loss, which denotes the loss resulting in the selection of the best of the first three recommended classifiers in comparison to the actual best-performing classifier among the considered set of classifiers.

\subsection{Mann-Whitney U Test}
too compare the ranking alternatives and to the basline to see if statistically significantly better.
